\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-05-04 letter-round2.tex
explain assumption 3 in letter

\vskip.3in
Some comments on substance, chronologically:
\begin{itemize}
\renewcommand\labelitemi{-}
	\item \textit{Assuming that lobbies represent only import-competing interests is a strong assumption and it requires theoretical and/or empirical justification.} \\
	Done, on page [8]
	\item \textit{Your model is static, so claiming that it rationalizes the four-year delay and eventual ratification of the US-SK FTA is a stretch. In particular, the interactions with automakers suggests a that a bargaining game under incomplete information would be more appropriate.} \\
	I have removed this claim.
  \item \textit{Your assumption that the identity of the median voter is not known a priori is standard in probability voting models, so you may want to stress the analogy between your setting and such models.}
  \item \textit{You claim that trade agreements act as a domestic political commitment device. To make this point formally, it would be nice to establish conditions under which, in equilibrium, “fast track authority” dominates cherry picking ex ante (in a version of your model with several import competing sectors).} \\
		I believe that I have already made this point formally in Result 3. The proof invokes Result 2 and Lemma 3 as it combines both dynamics that are explained intuitively in the text. I have made this more explicit by referring to those results in the text.

@@

  \item \textit{I don’t see how the move of Nature (which determines the probabilities o and o* is consistent with the idea that there is uncertainty about who is the median voter (which was part of your motivation). Assuming that o and o* are mutually exclusive is not great. It would be better to assume some timing (rather than have a simultaneous choice). Since the game is symmetric, assuming that Home’s legislature moves before Foreign’s would be without further loss of generality.}
  \item \textit{“the uncertainty about the median legislator’s identity is resolved.” What is this uncertainty really about?} \\
	This is explained in Section [currently 2.4, but will move], so I did not repeat it or reference it here in line with the earlier stylistic advice.

@@

  \item \textit{Assumption 2 does not formalize any intuition: it is just a labelling.} \\
	Quite right. The text has been modified appropriately.
  \item \textit{I feel uneasy about Assumption 3. I would rather have it as an outcome and, if it is not the only possibly one, a discussion of the conditions under which this arises.}
  \item \textit{The full separability of sectors implies very minimal interactions already. Assuming a fully symmetric model is then highly restrictive. How difficult would it be to relax the latter assumption?} \\
	It's not very hard to relax the symmetry of the \textit{equilibrium}, but it requires adding some restrictions so that the impact on the break probability from $\tau^{*a}$ in Lemma 2 does not outweigh that of $\tau^a$ in Lemma 1. I chose symmetry because it's prevalent in the literature (along with separability) and avoids such seemingly ad-hoc assumptions. I also take advantage of the symmetry for the argument establishing existence of the executives' problem and I'm not completely sure the most elegant way with the least additional restrictions to get that without symmetry.

>>>>

\vskip.3in
Some comments on substance, chronologically:
\begin{itemize}
\renewcommand\labelitemi{-}
	\item \textit{Assuming that lobbies represent only import-competing interests is a strong assumption and it requires theoretical and/or empirical justification.} \\
	Done, on page [8]
	\item \textit{Your model is static, so claiming that it rationalizes the four-year delay and eventual ratification of the US-SK FTA is a stretch. In particular, the interactions with automakers suggests a that a bargaining game under incomplete information would be more appropriate.} \\
	I have removed this claim.
  \item \textit{Your assumption that the identity of the median voter is not known a priori is standard in probability voting models, so you may want to stress the analogy between your setting and such models.}
  \item \textit{You claim that trade agreements act as a domestic political commitment device. To make this point formally, it would be nice to establish conditions under which, in equilibrium, ``fast track authority'' dominates cherry picking ex ante (in a version of your model with several import competing sectors).} \\
		I believe that I have already made this point formally in Result 3. The proof invokes Result 2 and Lemma 3 as it combines both dynamics that are explained intuitively in the text. I have made this more explicit by referring to those results in the text.

@@

  \item \textit{I don't see how the move of Nature (which determines the probabilities o and o* is consistent with the idea that there is uncertainty about who is the median voter (which was part of your motivation). Assuming that o and o* are mutually exclusive is not great. It would be better to assume some timing (rather than have a simultaneous choice). Since the game is symmetric, assuming that Home’s legislature moves before Foreign's would be without further loss of generality.}
  \item \textit{``the uncertainty about the median legislator's identity is resolved.'' What is this uncertainty really about?} \\
	This is explained in Section [currently 2.4, but will move], so I did not repeat it or reference it here in line with the earlier stylistic advice.

@@

  \item \textit{Assumption 2 does not formalize any intuition: it is just a labelling.} \\
	Quite right. The text has been modified appropriately.
  \item \textit{I feel uneasy about Assumption 3. I would rather have it as an outcome and, if it is not the only possibly one, a discussion of the conditions under which this arises.} \\
	I can remove Assumption 3, but the following happens: we get a second case for most of the results for when there are extreme realizations of $\theta$ such that the median legislator is more pro-trade than the executive at the trade-war phase so that the trade war tariffs are below the trade agreement tariffs. In this case, the results of the paper are uninteresting. So removing this assumption complicates the analysis and results without adding anything interesting or particularly realistic.

	Alternatively, I can make an assumption on the support of $\theta$ and the functional form of $\ga$ so that Assumption 3 becomes a result, but this seems overly restrictive to make the points of the paper.

  \item \textit{The full separability of sectors implies very minimal interactions already. Assuming a fully symmetric model is then highly restrictive. How difficult would it be to relax the latter assumption?} \\
	It's not very hard to relax the symmetry of the \textit{equilibrium}, but it requires adding some restrictions so that the impact on the break probability from $\tau^{*a}$ in Lemma 2 does not outweigh that of $\tau^a$ in Lemma 1. I chose symmetry because it's prevalent in the literature (along with separability) and avoids such seemingly ad-hoc assumptions. I also take advantage of the symmetry for the argument establishing existence of the executives' problem and I'm not completely sure the most elegant way with the least additional restrictions to get that without symmetry.
